Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-11-18 proposalPres.tex
Update proposalPres.tex
I added a timeline block and a frame break to the presentation, along with changing the font in the conclusion slide.
~
Added a parameter table in By-Wire Steering System

\begin{frame}{By-Wire Steering System Transfer Function}
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque A}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & 3.44E-16 \\
				b_1 & -2.203E-15 \\
				b_2 & 1.24E-13 \\
				b_3 & 5.975E-13 \\
				b_4 & 3.001E-12 \\
				b_5 & 5.23E-12 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 1.949E-16 \\
				a_1 & 1.455E-14 \\
				a_2 & 8.797E-13 \\
				a_3 & 2.304E-11 \\
				a_4 & 9.041E-10 \\
				a_5 & 9.01E-9 \\
				a_6 & 2.714E-7 \\
				a_7 & 9.241E-7 \\
				a_8 & 1.946E-5 \\
				a_9 & 3.889E-5 \\
				a_{10} & 0.0005721 \\
				a_{11} & 0.0008035 \\
				a_{12} & 0.008695 \\
				a_{13} & 0.008922 \\
				a_{14} & 0.07499 \\
				a_{15} & 0.05422 \\
				a_{16} & 0.3631 \\
				a_{17} & 0.1693 \\
				a_{18} & 0.9394 \\
				a_{19} & 0.2118 \\
				a_{20} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque B}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & -6.645E-15 \\
				b_1 & 2.161E-14 \\
				b_2 & -2.605E-14 \\
				b_3 & -4.744E-13 \\
				b_4 & -1.813E-13 \\
				b_5 & -4.858E-12 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 2.92E-15 \\
				a_1 & 2.758E-13 \\
				a_2 & 1.761E-11 \\
				a_3 & 4.228E-10 \\
				a_4 & 1.422E-8 \\
				a_5 & 1.561E-7 \\
				a_6 & 1.501E-6 \\
				a_7 & 8.426E-6 \\
				a_8 & 5.981E-5 \\
				a_9 & 0.0002016 \\
				a_{10} & 0.001226 \\
				a_{11} & 0.002649 \\
				a_{12} & 0.01456 \\
				a_{13} & 0.02044 \\
				a_{14} & 0.104 \\
				a_{15} & 0.09228 \\
				a_{16} & 0.4417 \\
				a_{17} & 0.2257 \\
				a_{18} & 1.025 \\
				a_{19} & 0.2305 \\
				a_{20} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}
\end{frame}

\begin{frame}{Manual Steering System Transfer Function}
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque A}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & 6.516E4 \\
				b_1 & -2.944E5 \\
				b_2 & 2.328E5 \\
				b_3 & -2.487E5 \\
				b_4 & 8.25E4 \\
				b_5 & -3.038E4 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 1.224E5 \\
				a_1 & 4.227E5 \\
				a_2 & 2.202E6 \\
				a_3 & 3.54E6 \\
				a_4 & 7.98E6 \\
				a_5 & 7.62E5 \\
				a_6 & 1.071E7 \\
				a_7 & 6.745E6 \\
				a_8 & 6.85E6 \\
				a_9 & 3.006E6 \\
				a_{10} & 2.365E6 \\
				a_{11} & 7.37E5 \\
				a_{12} & 4.669E5 \\
				a_{13} & 1.021E5 \\
				a_{14} & 5.319E4 \\
				a_{15} & 7752 \\
				a_{16} & 3353 \\
				a_{17} & 287.5 \\
				a_{18} & 102.4 \\
				a_{19} & 3.653 \\
				a_{20} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque B}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & 1.209E4 \\
				b_1 & 1.855E5 \\
				b_2 & -2.801E5 \\
				b_3 & 4.72E5 \\
				b_4 & -3.976E4 \\
				b_5 & 7.693E4 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 4.687E4 \\
				a_1 & 7.037E5 \\
				a_2 & 2.624E6 \\
				a_3 & 6.133E6 \\
				a_4 & 1.197E7 \\
				a_5 & 1.487E7 \\
				a_6 & 1.887E7 \\
				a_7 & 1.446E7 \\
				a_8 & 1.314E7 \\
				a_9 & 7.01E6 \\
				a_{10} & 4.79E6 \\
				a_{11} & 1.886E6 \\
				a_{12} & 9.836E5 \\
				a_{13} & 2.937E5 \\
				a_{14} & 1.149E5 \\
				a_{15} & 2.617E4 \\
				a_{16} & 7205 \\
				a_{17} & 1232 \\
				a_{18} & 200 \\
				a_{19} & 23.54 \\
				a_{20} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}
\end{frame}

@@

\begin{frame}{Manual Acceleration System Transfer Function}
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque A}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & -5.741E6 \\
				b_1 & -2.644E7 \\
				b_2 & -2.797E6 \\
				b_3 & -1.304E7 \\
				b_4 & -3.203E6 \\
				b_5 & -1.159E6 \\
				b_6 & -5.519E5 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 2.307E7 \\
				a_1 & 8.369E7 \\
				a_2 & 9.137E8 \\
				a_3 & 1.992E9 \\
				a_4 & 3.753E9 \\
				a_5 & 5.454E9 \\
				a_6 & 5.548E9 \\
				a_7 & 5.869E9 \\
				a_8 & 3.453E9 \\
				a_9 & 3.161E9 \\
				a_{10} & 1.54E9 \\
				a_{11} & 9.654E8 \\
				a_{12} & 3.556E8 \\
				a_{13} & 1.789E8 \\
				a_{14} & 5.082E7 \\
				a_{15} & 2.071E7 \\
				a_{16} & 4.569E6 \\
				a_{17} & 1.498E6 \\
				a_{18} & 2.553E5 \\
				a_{19} & 6.532E4 \\
				a_{20} & 8443 \\
				a_{21} & 1559 \\
				a_{22} & 147.3 \\
				a_{23} & 15.5 \\
				a_{24} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque B}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & -4.159E6 \\
				b_1 & 1.851E6 \\
				b_2 & -4.457E6 \\
				b_3 & 9.043E5 \\
				b_4 & -7.45E5 \\
				b_5 & 1.865E5 \\
				b_6 & -1.545E4 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 5.224E6 \\
				a_1 & 4.205E7 \\
				a_2 & 1.429E8 \\
				a_3 & 3.233E8 \\
				a_4 & 5.444E8 \\
				a_5 & 7.326E8 \\
				a_6 & 8.247E8 \\
				a_7 & 7.402E8 \\
				a_8 & 6.301E8 \\
				a_9 & 3.99E8 \\
				a_{10} & 2.731E8 \\
				a_{11} & 1.264E8 \\
				a_{12} & 7.223E7 \\
				a_{13} & 2.48E7 \\
				a_{14} & 1.216E7 \\
				a_{15} & 3.084E6 \\
				a_{16} & 1.324E6 \\
				a_{17} & 2.422E5 \\
				a_{18} & 9.264E4 \\
				a_{19} & 1.159E4 \\
				a_{20} & 4003 \\
				a_{21} & 307.4 \\
				a_{22} & 96.87 \\
				a_{23} & 3.451 \\
				a_{24} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}
\end{frame}

@@

\begin{frame}{Timeline and Milestones}
  \begin{block}{Milestones}
 \begin{itemize}
        \item Model steering subsystem 
	\item Test subsystem models with HIL system 
	\item Final report and presentation 
\end{itemize}
  \end{block}
\end{frame}

@@

\section{Concluding Remarks}
\begin{frame}{Concluding Remarks}
  \begin{block}{Project goals}
    \begin{LARGE}
      \begin{itemize}
        \item Develop models of an autonomous vehicle's subsystems
        \begin{itemize}
          \item Steering Model
          \item Acceleration Model
          \item Brake Model
          \item Shift Model
          \item Speed Model
          \item Speed Control Model
        \end{itemize}
      \end{itemize}
    \end{LARGE}
  \end{block}
  \begin{block}{Anticipated Challenges}
    \begin{itemize}
      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}{References}

>>>>

\begin{frame}{By-Wire Steering System Transfer Function}

  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$&$a_{19}$&$a_{20}$\\
      \midrule
      1.949E-16 & 1.455E-14 & 8.797E-13 & 2.304E-11 & 9.041E-10 & 9.01E-9 & 2.714E-7 & 9.241E-7 & 1.946E-5 & 3.889E-5 & 0.0005721 & 0.0008035 & 0.008695 & 0.008922 & 0.07499 & 0.05422 & 0.3631 & 0.1693 & 0.9394 & 0.2118 & 1\\
      \bottomrule
    \end{tabular}}

% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque A}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & 3.44E-16 \\
% 				b_1 & -2.203E-15 \\
% 				b_2 & 1.24E-13 \\
% 				b_3 & 5.975E-13 \\
% 				b_4 & 3.001E-12 \\
% 				b_5 & 5.23E-12 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 1.949E-16 \\
% 				a_1 & 1.455E-14 \\
% 				a_2 & 8.797E-13 \\
% 				a_3 & 2.304E-11 \\
% 				a_4 & 9.041E-10 \\
% 				a_5 & 9.01E-9 \\
% 				a_6 & 2.714E-7 \\
% 				a_7 & 9.241E-7 \\
% 				a_8 & 1.946E-5 \\
% 				a_9 & 3.889E-5 \\
% 				a_{10} & 0.0005721 \\
% 				a_{11} & 0.0008035 \\
% 				a_{12} & 0.008695 \\
% 				a_{13} & 0.008922 \\
% 				a_{14} & 0.07499 \\
% 				a_{15} & 0.05422 \\
% 				a_{16} & 0.3631 \\
% 				a_{17} & 0.1693 \\
% 				a_{18} & 0.9394 \\
% 				a_{19} & 0.2118 \\
% 				a_{20} & 1 \\
% 				\hline
% 			\end{tabular} 
% 		\end{tabular}
% 	\end{block}
% \end{minipage}%
% \hfill%
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque B}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & -6.645E-15 \\
% 				b_1 & 2.161E-14 \\
% 				b_2 & -2.605E-14 \\
% 				b_3 & -4.744E-13 \\
% 				b_4 & -1.813E-13 \\
% 				b_5 & -4.858E-12 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 2.92E-15 \\
% 				a_1 & 2.758E-13 \\
% 				a_2 & 1.761E-11 \\
% 				a_3 & 4.228E-10 \\
% 				a_4 & 1.422E-8 \\
% 				a_5 & 1.561E-7 \\
% 				a_6 & 1.501E-6 \\
% 				a_7 & 8.426E-6 \\
% 				a_8 & 5.981E-5 \\
% 				a_9 & 0.0002016 \\
% 				a_{10} & 0.001226 \\
% 				a_{11} & 0.002649 \\
% 				a_{12} & 0.01456 \\
% 				a_{13} & 0.02044 \\
% 				a_{14} & 0.104 \\
% 				a_{15} & 0.09228 \\
% 				a_{16} & 0.4417 \\
% 				a_{17} & 0.2257 \\
% 				a_{18} & 1.025 \\
% 				a_{19} & 0.2305 \\
% 				a_{20} & 1 \\
% 				\hline
% 			\end{tabular} 
% 		\end{tabular}
% 	\end{block}
% \end{minipage}
\end{frame}

\begin{frame}{Manual Steering System Transfer Function}
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque A}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & 6.516E4 \\
% 				b_1 & -2.944E5 \\
% 				b_2 & 2.328E5 \\
% 				b_3 & -2.487E5 \\
% 				b_4 & 8.25E4 \\
% 				b_5 & -3.038E4 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 1.224E5 \\
% 				a_1 & 4.227E5 \\
% 				a_2 & 2.202E6 \\
% 				a_3 & 3.54E6 \\
% 				a_4 & 7.98E6 \\
% 				a_5 & 7.62E5 \\
% 				a_6 & 1.071E7 \\
% 				a_7 & 6.745E6 \\
% 				a_8 & 6.85E6 \\
% 				a_9 & 3.006E6 \\
% 				a_{10} & 2.365E6 \\
% 				a_{11} & 7.37E5 \\
% 				a_{12} & 4.669E5 \\
% 				a_{13} & 1.021E5 \\
% 				a_{14} & 5.319E4 \\
% 				a_{15} & 7752 \\
% 				a_{16} & 3353 \\
% 				a_{17} & 287.5 \\
% 				a_{18} & 102.4 \\
% 				a_{19} & 3.653 \\
% 				a_{20} & 1 \\
% 				\hline
% 			\end{tabular} \\
% 		\end{tabular}
% 	\end{block}
% \end{minipage}%
% \hfill%
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque B}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & 1.209E4 \\
% 				b_1 & 1.855E5 \\
% 				b_2 & -2.801E5 \\
% 				b_3 & 4.72E5 \\
% 				b_4 & -3.976E4 \\
% 				b_5 & 7.693E4 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 4.687E4 \\
% 				a_1 & 7.037E5 \\
% 				a_2 & 2.624E6 \\
% 				a_3 & 6.133E6 \\
% 				a_4 & 1.197E7 \\
% 				a_5 & 1.487E7 \\
% 				a_6 & 1.887E7 \\
% 				a_7 & 1.446E7 \\
% 				a_8 & 1.314E7 \\
% 				a_9 & 7.01E6 \\
% 				a_{10} & 4.79E6 \\
% 				a_{11} & 1.886E6 \\
% 				a_{12} & 9.836E5 \\
% 				a_{13} & 2.937E5 \\
% 				a_{14} & 1.149E5 \\
% 				a_{15} & 2.617E4 \\
% 				a_{16} & 7205 \\
% 				a_{17} & 1232 \\
% 				a_{18} & 200 \\
% 				a_{19} & 23.54 \\
% 				a_{20} & 1 \\
% 				\hline
% 			\end{tabular} \\
% 		\end{tabular}
% 	\end{block}
% \end{minipage}
\end{frame}

@@

\begin{frame}{Manual Acceleration System Transfer Function}
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque A}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & -5.741E6 \\
% 				b_1 & -2.644E7 \\
% 				b_2 & -2.797E6 \\
% 				b_3 & -1.304E7 \\
% 				b_4 & -3.203E6 \\
% 				b_5 & -1.159E6 \\
% 				b_6 & -5.519E5 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 2.307E7 \\
% 				a_1 & 8.369E7 \\
% 				a_2 & 9.137E8 \\
% 				a_3 & 1.992E9 \\
% 				a_4 & 3.753E9 \\
% 				a_5 & 5.454E9 \\
% 				a_6 & 5.548E9 \\
% 				a_7 & 5.869E9 \\
% 				a_8 & 3.453E9 \\
% 				a_9 & 3.161E9 \\
% 				a_{10} & 1.54E9 \\
% 				a_{11} & 9.654E8 \\
% 				a_{12} & 3.556E8 \\
% 				a_{13} & 1.789E8 \\
% 				a_{14} & 5.082E7 \\
% 				a_{15} & 2.071E7 \\
% 				a_{16} & 4.569E6 \\
% 				a_{17} & 1.498E6 \\
% 				a_{18} & 2.553E5 \\
% 				a_{19} & 6.532E4 \\
% 				a_{20} & 8443 \\
% 				a_{21} & 1559 \\
% 				a_{22} & 147.3 \\
% 				a_{23} & 15.5 \\
% 				a_{24} & 1 \\
% 				\hline
% 			\end{tabular} \\
% 		\end{tabular}
% 	\end{block}
% \end{minipage}%
% \hfill%
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque B}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & -4.159E6 \\
% 				b_1 & 1.851E6 \\
% 				b_2 & -4.457E6 \\
% 				b_3 & 9.043E5 \\
% 				b_4 & -7.45E5 \\
% 				b_5 & 1.865E5 \\
% 				b_6 & -1.545E4 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 5.224E6 \\
% 				a_1 & 4.205E7 \\
% 				a_2 & 1.429E8 \\
% 				a_3 & 3.233E8 \\
% 				a_4 & 5.444E8 \\
% 				a_5 & 7.326E8 \\
% 				a_6 & 8.247E8 \\
% 				a_7 & 7.402E8 \\
% 				a_8 & 6.301E8 \\
% 				a_9 & 3.99E8 \\
% 				a_{10} & 2.731E8 \\
% 				a_{11} & 1.264E8 \\
% 				a_{12} & 7.223E7 \\
% 				a_{13} & 2.48E7 \\
% 				a_{14} & 1.216E7 \\
% 				a_{15} & 3.084E6 \\
% 				a_{16} & 1.324E6 \\
% 				a_{17} & 2.422E5 \\
% 				a_{18} & 9.264E4 \\
% 				a_{19} & 1.159E4 \\
% 				a_{20} & 4003 \\
% 				a_{21} & 307.4 \\
% 				a_{22} & 96.87 \\
% 				a_{23} & 3.451 \\
% 				a_{24} & 1 \\
% 				\hline
% 			\end{tabular} \\
% 		\end{tabular}
% 	\end{block}
% \end{minipage}
\end{frame}

@@

\begin{frame}{Timeline and Milestones}
  \begin{block}{Milestones}
 \begin{itemize}
        \item Model steering subsystem 
	\item Test subsystem models with HIL system 
	\item Final report and presentation 
\end{itemize}
  \end{block}

  \begin{block}{Timeline}
  \begin{itemize}
  \item Fall Semester
  \begin{itemize}
	\begin{tiny}
	\item System Identification Documentation 
	\item Collect Steering, Acceleration, and Brake Data 
	\item System Identification Tutorials
	\item System Functional Requirements Document and Presentation
	\item Proposal Document and Presentation 
	\item Model Steering, Acceleration, and Brake Subsystems 
	\end{tiny}
	\end{itemize}
	\item Spring Semester
	\begin{itemize}
	\begin{tiny}
	\item Collect Shift, Speed Control, and Speed Data  
	\item Model Shift, Speed Control, and Speed Subsystems  
	\item Test Subsystems
	\item Test Subsystems with HIL
	\item Final Report and Presentation 
	\item IAB Presentation 
	\item Project Demonstration  
	\end{tiny}
	\end{itemize}
	\end{itemize}
  \end{block}

@@

\section{Concluding Remarks}
\begin{frame}{Concluding Remarks}
  \begin{block}{Project goals}
    %\begin{LARGE}
      \begin{itemize}
        \item Develop models of an autonomous vehicle's subsystems
        \begin{itemize}
          \item Steering Model
          \item Acceleration Model
          \item Brake Model
          \item Shift Model
          \item Speed Model
          \item Speed Control Model
        \end{itemize}
      \end{itemize}
    %\end{LARGE}
  \end{block}
  \begin{block}{Anticipated Challenges}
    \begin{itemize}
      \item Achieving an acceptable accuracy and reliability for each model due to nonlinearities over small changes
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}[allowframebreaks]{References}
